### 2016-12-22 analysis-note-vf/Appendix.tex
update the analysis note with the latest plots for both DVCS channels
update the He4 pid plots and the appendix with the new free proton fitting.

\chapter{$A_{LU}$ tables}
\begin{table}[!h]
   \begin{center}
      \begin{tabular}{||l|l|l|l|l||}
         \hline
 $<Q^{2}>$ & $<x_{B}>$ & $<-t>$ & $<\phi>$ & $A_{LU}$ $\pm$ stat. $\pm$ syst.\\
         \hline
  1.143 & 0.136 & 0.096 &  23.4  &  0.1407   $\pm$ 0.0800   $\pm$  0.0257 \\
  1.143 & 0.136 & 0.096 &  59.9  &  0.3563   $\pm$ 0.0687   $\pm$  0.0188 \\
  1.143 & 0.136 & 0.096 &  97.6  &  0.4241   $\pm$ 0.0870   $\pm$  0.0403 \\
  1.143 & 0.136 & 0.096 &  139.9 &  0.1576   $\pm$ 0.1344   $\pm$  0.0267 \\
  1.143 & 0.136 & 0.096 &  179.1 &  0.1496   $\pm$ 0.1390   $\pm$  0.0278 \\
  1.143 & 0.136 & 0.096 &  218.9 & -0.1361   $\pm$ 0.1123   $\pm$  0.0248 \\
  1.143 & 0.136 & 0.096 &  263.5 & -0.3384   $\pm$ 0.0922   $\pm$  0.0389 \\
  1.143 & 0.136 & 0.096 &  302.9 & -0.1731   $\pm$ 0.0722   $\pm$  0.0263 \\
  1.143 & 0.136 & 0.096 &  337.5 & -0.3439   $\pm$ 0.0744   $\pm$  0.0343 \\
  \hline                                                           
  1.423 & 0.172 & 0.099 &  19.9  &  0.1538   $\pm$ 0.0650   $\pm$  0.0267 \\
  1.423 & 0.172 & 0.099 &  57.3  &  0.2941   $\pm$ 0.0684   $\pm$  0.0250 \\
  1.423 & 0.172 & 0.099 &  95.4  &  0.4352   $\pm$ 0.0997   $\pm$  0.0426 \\
  1.423 & 0.172 & 0.099 &  138.3 &  0.1251   $\pm$ 0.1418   $\pm$  0.0250 \\
  1.423 & 0.172 & 0.099 &  181.2 &  0.2139   $\pm$ 0.1813   $\pm$  0.0302 \\
  1.423 & 0.172 & 0.099 &  220.3 & -0.2494   $\pm$ 0.1646   $\pm$  0.0344 \\
  1.423 & 0.172 & 0.099 &  263.4 & -0.3187   $\pm$ 0.1128   $\pm$  0.0366 \\
  1.423 & 0.172 & 0.099 &  302.5 & -0.3429   $\pm$ 0.0695   $\pm$  0.0383 \\
  1.423 & 0.172 & 0.099 &  338.1 & -0.1382   $\pm$ 0.0680   $\pm$  0.0261 \\
  \hline                                                                    
  1.902 & 0.224 & 0.107 &  21.0  &  0.0904   $\pm$ 0.0630   $\pm$  0.0234 \\
  1.902 & 0.224 & 0.107 &  56.6  &  0.3647   $\pm$ 0.0654   $\pm$  0.0185 \\
  1.902 & 0.224 & 0.107 &  95.7  &  0.1701   $\pm$ 0.1072   $\pm$  0.0173 \\
  1.902 & 0.224 & 0.107 &  139.6 &  0.0994   $\pm$ 0.1732   $\pm$  0.0170 \\
  1.902 & 0.224 & 0.107 &  179.5 & -0.0855   $\pm$ 0.2165   $\pm$  0.0126 \\
  1.902 & 0.224 & 0.107 &  221.6 & -0.1338   $\pm$ 0.1825   $\pm$  0.0152 \\
  1.902 & 0.224 & 0.107 &  262.7 & -0.2772   $\pm$ 0.1185   $\pm$  0.0260 \\
  1.902 & 0.224 & 0.107 &  303.5 & -0.2306   $\pm$ 0.0745   $\pm$  0.0207 \\
  1.902 & 0.224 & 0.107 &  339.2 & -0.1958   $\pm$ 0.0607   $\pm$  0.0163 \\
         \hline \hline
      \end{tabular}
      \caption{ The coherent $A_{LU}$ in $Q^2$ bins}
      \label{table:Coh_Q2_BSA}
   \end{center}
\end{table}

@@

  1.164 & 0.132 & 0.095 & 24.7   &  0.0165   $\pm$ 0.0983    $\pm$   0.0221 \\
  1.164 & 0.132 & 0.095 & 60.5   &  0.3681   $\pm$ 0.0657    $\pm$   0.0198 \\
  1.164 & 0.132 & 0.095 & 97.8   &  0.4334   $\pm$ 0.0805    $\pm$   0.0408 \\
  1.164 & 0.132 & 0.095 & 140.4  &  0.2580   $\pm$ 0.1277    $\pm$   0.0333 \\
  1.164 & 0.132 & 0.095 & 178.8  &  0.1732   $\pm$ 0.1341    $\pm$   0.0293 \\
  1.164 & 0.132 & 0.095 & 218.2  & -0.1259   $\pm$ 0.1077    $\pm$   0.0243 \\
  1.164 & 0.132 & 0.095 & 263.5  & -0.3176   $\pm$ 0.0852    $\pm$   0.0372 \\
  1.164 & 0.132 & 0.095 & 302.0  & -0.1521   $\pm$ 0.0661    $\pm$   0.0259 \\
  1.164 & 0.132 & 0.095 & 335.4  & -0.2915   $\pm$ 0.0885    $\pm$   0.0319 \\
   \hline                                                                     
  1.439 & 0.17 & 0.099 & 21.1    &  0.1815   $\pm$ 0.0628    $\pm$   0.0230 \\
  1.439 & 0.17 & 0.099 &  57.0   &  0.2075   $\pm$ 0.0672    $\pm$   0.0195 \\
  1.439 & 0.17 & 0.099 &  95.1   &  0.3013   $\pm$ 0.1042    $\pm$   0.0295 \\
  1.439 & 0.17 & 0.099 &  137.9  &  0.0939   $\pm$ 0.1335    $\pm$   0.0187 \\
  1.439 & 0.17 & 0.099 &  181.1  &  0.0167   $\pm$ 0.1741    $\pm$   0.0197 \\
  1.439 & 0.17 & 0.099 &  221.0  & -0.2219   $\pm$ 0.1641    $\pm$   0.0270 \\
  1.439 & 0.17 & 0.099 &  264.4  & -0.2657   $\pm$ 0.1120    $\pm$   0.0292 \\
  1.439 & 0.17 & 0.099 &  302.9  & -0.3816   $\pm$ 0.0716    $\pm$   0.0331 \\
  1.439 & 0.17 & 0.099 &  338.0  & -0.2336   $\pm$ 0.0657    $\pm$   0.0254 \\
   \hline                                                                     
  1.844 & 0.225 & 0.107 & 19.9   &  0.1286   $\pm$ 0.0601    $\pm$   0.0248 \\
  1.844 & 0.225 & 0.107 & 56.1   &  0.4551   $\pm$ 0.0713    $\pm$   0.0224 \\
  1.844 & 0.225 & 0.107 & 95.3   &  0.2540   $\pm$ 0.1201    $\pm$   0.0271 \\
  1.844 & 0.225 & 0.107 & 139.6  & -0.1136   $\pm$ 0.2150    $\pm$   0.0166 \\
  1.844 & 0.225 & 0.107 & 180.6  &  0.1414   $\pm$ 0.2634    $\pm$   0.0204 \\
  1.844 & 0.225 & 0.107 & 223.7  & -0.2158   $\pm$ 0.2097    $\pm$   0.0270 \\
  1.844 & 0.225 & 0.107 & 260.6  & -0.3623   $\pm$ 0.1442    $\pm$   0.0353 \\
  1.844 & 0.225 & 0.107 & 304.4  & -0.2359   $\pm$ 0.0814    $\pm$   0.0263 \\
  1.844 & 0.225 & 0.107 & 340.0  & -0.1393   $\pm$ 0.0593    $\pm$   0.0175 \\

@@

\begin{table}[!h]
   \begin{center}
      \begin{tabular}{||l|l|l|l|l||}
         \hline
 $<Q^{2}>$ & $<x_{B}>$ & $<-t>$ & $<\phi>$ & $A_{LU}$ $\pm$ stat. $\pm$ syst.\\
         \hline
  1.36 & 0.160 & 0.080 &  21.3   &  0.1692   $\pm$ 0.0708    $\pm$  0.0263  \\
  1.36 & 0.160 & 0.080 &  57.2   &  0.2972   $\pm$ 0.0644    $\pm$  0.0243  \\
  1.36 & 0.160 & 0.080 &  95.9   &  0.4170   $\pm$ 0.0954    $\pm$  0.0394  \\
  1.36 & 0.160 & 0.080 &  138.1  &  0.1374   $\pm$ 0.1434    $\pm$  0.0252  \\
  1.36 & 0.160 & 0.080 &  179.2  &  0.3245   $\pm$ 0.1657    $\pm$  0.0371  \\
  1.36 & 0.160 & 0.080 &  221.6  & -0.2851   $\pm$ 0.1376    $\pm$  0.0370  \\
  1.36 & 0.160 & 0.080 &  265.6  & -0.4009   $\pm$ 0.1050    $\pm$  0.0403  \\
  1.36 & 0.160 & 0.080 &  301.6  & -0.2257   $\pm$ 0.0746    $\pm$  0.0294  \\
  1.36 & 0.160 & 0.080 &  339.7  & -0.2312   $\pm$ 0.0637    $\pm$  0.0281  \\
\hline                                                              
  1.507 & 0.179 & 0.094 & 21.2   &  0.1593   $\pm$ 0.0696    $\pm$  0.0267  \\
  1.507 & 0.179 & 0.094 & 57.0   &  0.3607   $\pm$ 0.0679    $\pm$  0.0284  \\
  1.507 & 0.179 & 0.094 & 97.0   &  0.2913   $\pm$ 0.0971    $\pm$  0.0307  \\
  1.507 & 0.179 & 0.094 & 141.6  &  0.1033   $\pm$ 0.1621    $\pm$  0.0215  \\
  1.507 & 0.179 & 0.094 & 179.6  & -0.3610   $\pm$ 0.1755    $\pm$  0.0360  \\
  1.507 & 0.179 & 0.094 & 220.1  & -0.0705   $\pm$ 0.1583    $\pm$  0.0147  \\
  1.507 & 0.179 & 0.094 & 262.5  & -0.1960   $\pm$ 0.1079    $\pm$  0.0283  \\
  1.507 & 0.179 & 0.094 & 303.5  & -0.2605   $\pm$ 0.0763    $\pm$  0.0286  \\
  1.507 & 0.179 & 0.094 & 338.2  & -0.1241   $\pm$ 0.0700    $\pm$  0.0201  \\
\hline                                                                         
  1.610 & 0.193 & 0.127 & 21.0   &  0.0248   $\pm$ 0.0675    $\pm$  0.0214  \\
  1.610 & 0.193 & 0.127 & 59.4   &  0.3820   $\pm$ 0.0725    $\pm$  0.0204  \\
  1.610 & 0.193 & 0.127 & 95.8   &  0.3454   $\pm$ 0.1021    $\pm$  0.0313  \\
  1.610 & 0.193 & 0.127 & 138.6  &  0.1427   $\pm$ 0.1440    $\pm$  0.0203  \\
  1.610 & 0.193 & 0.127 & 180.4  &  0.3198   $\pm$ 0.1557    $\pm$  0.0354  \\
  1.610 & 0.193 & 0.127 & 218.4  & -0.0996   $\pm$ 0.1403    $\pm$  0.0189  \\
  1.610 & 0.193 & 0.127 & 261.4  & -0.3095   $\pm$ 0.1103    $\pm$  0.0327  \\
  1.610 & 0.193 & 0.127 & 303.3  & -0.2537   $\pm$ 0.0689    $\pm$  0.0280  \\
  1.610 & 0.193 & 0.127 & 337.2  & -0.2732   $\pm$ 0.0703    $\pm$  0.0261  \\

@@

\chapter{Free proton beam-spin asymmetry interpolation} 
\label{app:free-proton-alu}
\section{Fitting the experimentally measured asymmetries} \label{fit_int} 
Following the discussion in section \ref{sec:Generalized_EMC}, comparing the 
coherent and the incoherent beam-spin asymmetries to free proton asymmetries 
reveal new information about the nuclear medium modifications. To construct 
such ratio, the published free proton asymmetries \cite{FX_BSA} have been used 
in this analysis, see figure \ref{fig:free-proton-alu}. The measured free 
proton $A_{LU}$ at $\phi = 90^{\circ}$ were fitted as a function of $-t$ for 
the different bins in $x_B$ and $Q^2$. Then, the parameters of the fits were 
parametrized as a function of $x_B$ assuming that the dependence on $Q^2$ is 
negligible, figure \ref{fig:free-proton-alu}. Finally, the free proton 
asymmetries were calculated at the same measured incoherent and coherent
kinematic values.  The statistical errors on the calculated asymmetries were 
calculated using the error bars on the fitted parameters $a_{i}$s.\\

\begin{figure}[tpb]
\centering
\includegraphics[scale=0.85]{fig_updated/ALU-proton-fits.pdf}
\caption{Black circles are the free proton beam-spin asymmetries at $\phi = 90 
   ^{\circ}$ as a function of $-t$ in different ($x_B, Q^2$) bins as measured 
   at CLAS-E1DVCS experiment. The solid red curves are fits to the free proton 
   asymmetries in the form $a_{0}*(\sqrt{t}-a_{1})*e^{a_{2}*\sqrt{t} - a_{3}}$.  
   The dashed curves are calculations using the fitted $a_{i}$'s parameters as 
a function of $x_B$ as shown in figure \ref{fig:fitted-points-xB}. Blue points 
are the interpolated points corresponding for the incoherent points presented 
in this analysis. The red points stand for the extrapolated free proton 
asymmetries at the measured coherent kinematics.}
\label{fig:free-proton-alu}
\end{figure}

\begin{figure}[tpb]
\includegraphics[scale=0.37]{fig_updated/test_a0.pdf}
\includegraphics[scale=0.37]{fig_updated/test_a1.pdf}
\includegraphics[scale=0.37]{fig_updated/test_a2.pdf}
\hspace{1.7cm}
\includegraphics[scale=0.37]{fig_updated/test_a3.pdf}
\caption{The fitted $a_0$, $a_1$, $a_2$, and $a_3$ parameters as a function of 
$x_B$.}
\label{fig:fitted-points-xB}
\end{figure}

>>>>

\chapter{$A_{LU}$ tables}
\begin{table}[!h]
   \begin{center}
      \begin{tabular}{||l|l|l|l|l||}
         \hline
 $<Q^{2}>$ & $<x_{B}>$ & $<-t>$ & $<\phi>$ & $A_{LU}$ $\pm$ stat. $\pm$ syst.\\
         \hline
  1.143 & 0.136 & 0.096 & 24.0  &  0.1575 $\pm$  0.1016 $\pm$ 0.0257 \\
  1.143 & 0.136 & 0.096 & 60.0  &  0.3656 $\pm$  0.0903 $\pm$ 0.0188 \\
  1.143 & 0.136 & 0.096 & 98.5  &  0.3586 $\pm$  0.1051 $\pm$ 0.0403 \\
  1.143 & 0.136 & 0.096 & 141.2 &  0.1498 $\pm$  0.1645 $\pm$ 0.0267 \\
  1.143 & 0.136 & 0.096 & 177.7 &  0.1849 $\pm$  0.1664 $\pm$ 0.0278 \\
  1.143 & 0.136 & 0.096 & 219.3 &  0.0555 $\pm$  0.1475 $\pm$ 0.0248 \\
  1.143 & 0.136 & 0.096 & 263.4 & -0.3184 $\pm$  0.1171 $\pm$ 0.0389 \\
  1.143 & 0.136 & 0.096 & 302.7 & -0.1160 $\pm$  0.0975 $\pm$ 0.0263 \\
  1.143 & 0.136 & 0.096 & 337.9 & -0.2805 $\pm$  0.0952 $\pm$ 0.0343 \\
  \hline                                                               
  1.423 & 0.172 & 0.099 & 21.1  &  0.1694 $\pm$  0.0858 $\pm$ 0.0267 \\
  1.423 & 0.172 & 0.099 & 55.9  &  0.2889 $\pm$  0.0859 $\pm$ 0.0250 \\
  1.423 & 0.172 & 0.099 & 96.7  &  0.4761 $\pm$  0.1304 $\pm$ 0.0426 \\
  1.423 & 0.172 & 0.099 & 138.9 &  0.2134 $\pm$  0.1784 $\pm$ 0.0250 \\
  1.423 & 0.172 & 0.099 & 179.8 &  0.2996 $\pm$  0.1967 $\pm$ 0.0302 \\
  1.423 & 0.172 & 0.099 & 218.7 & -0.2375 $\pm$  0.1913 $\pm$ 0.0344 \\
  1.423 & 0.172 & 0.099 & 263.5 & -0.2521 $\pm$  0.1398 $\pm$ 0.0366 \\
  1.423 & 0.172 & 0.099 & 302.6 & -0.3526 $\pm$  0.0855 $\pm$ 0.0383 \\
  1.423 & 0.172 & 0.099 & 338.0 & -0.2344 $\pm$  0.0801 $\pm$ 0.0261 \\
  \hline                                                               
  1.902 & 0.224 & 0.107 & 21.0  &  0.1626 $\pm$  0.0779 $\pm$ 0.0234 \\
  1.902 & 0.224 & 0.107 & 56.4  &  0.3433 $\pm$  0.0817 $\pm$ 0.0185 \\
  1.902 & 0.224 & 0.107 & 95.9  &  0.2443 $\pm$  0.1270 $\pm$ 0.0173 \\
  1.902 & 0.224 & 0.107 & 138.6 &  0.4026 $\pm$  0.2333 $\pm$ 0.0170 \\
  1.902 & 0.224 & 0.107 & 179.8 &  0.0514 $\pm$  0.2906 $\pm$ 0.0126 \\
  1.902 & 0.224 & 0.107 & 222.7 & -0.0281 $\pm$  0.2275 $\pm$ 0.0152 \\
  1.902 & 0.224 & 0.107 & 264.5 & -0.2909 $\pm$  0.1379 $\pm$ 0.0260 \\
  1.902 & 0.224 & 0.107 & 303.5 & -0.1011 $\pm$  0.0940 $\pm$ 0.0207 \\
  1.902 & 0.224 & 0.107 & 338.9 & -0.1661 $\pm$  0.0773 $\pm$ 0.0163 \\
         \hline \hline
      \end{tabular}
      \caption{ The coherent $A_{LU}$ in $Q^2$ bins}
      \label{table:Coh_Q2_BSA}
   \end{center}
\end{table}

@@

  1.164 & 0.132 & 0.095 & 25.4  &  0.0441 $\pm$ 0.1329 $\pm$ 0.0221 \\
  1.164 & 0.132 & 0.095 & 60.8  &  0.4030 $\pm$ 0.0865 $\pm$ 0.0198 \\
  1.164 & 0.132 & 0.095 & 98.6  &  0.3878 $\pm$ 0.0984 $\pm$ 0.0408 \\
  1.164 & 0.132 & 0.095 & 141.7 &  0.2957 $\pm$ 0.1524 $\pm$ 0.0333 \\
  1.164 & 0.132 & 0.095 & 177.2 &  0.2646 $\pm$ 0.1599 $\pm$ 0.0293 \\
  1.164 & 0.132 & 0.095 & 218.4 &  0.0127 $\pm$ 0.1364 $\pm$ 0.0243 \\
  1.164 & 0.132 & 0.095 & 263.2 & -0.2955 $\pm$ 0.1063 $\pm$ 0.0372 \\
  1.164 & 0.132 & 0.095 & 301.6 & -0.1121 $\pm$ 0.0868 $\pm$ 0.0259 \\
  1.164 & 0.132 & 0.095 & 335.6 & -0.1940 $\pm$ 0.1149 $\pm$ 0.0319 \\
   \hline                                                             
  1.439 & 0.17 & 0.099 &  22.8  &  0.1597 $\pm$ 0.0820 $\pm$ 0.0230 \\
  1.439 & 0.17 & 0.099 &  55.9  &  0.1592 $\pm$ 0.0857 $\pm$ 0.0195 \\
  1.439 & 0.17 & 0.099 &  96.7  &  0.2178 $\pm$ 0.1320 $\pm$ 0.0295 \\
  1.439 & 0.17 & 0.099 &  138.7 &  0.3251 $\pm$ 0.1763 $\pm$ 0.0187 \\
  1.439 & 0.17 & 0.099 &  180.0 & -0.0093 $\pm$ 0.1947 $\pm$ 0.0197 \\
  1.439 & 0.17 & 0.099 &  219.8 & -0.1457 $\pm$ 0.2000 $\pm$ 0.0270 \\
  1.439 & 0.17 & 0.099 &  265.0 & -0.2163 $\pm$ 0.1374 $\pm$ 0.0292 \\
  1.439 & 0.17 & 0.099 &  302.9 & -0.3729 $\pm$ 0.0907 $\pm$ 0.0331 \\
  1.439 & 0.17 & 0.099 &  337.9 & -0.2505 $\pm$ 0.0791 $\pm$ 0.0254 \\
   \hline                                                             
  1.844 & 0.225 & 0.107 & 19.8  &  0.2355 $\pm$ 0.0732 $\pm$ 0.0248 \\
  1.844 & 0.225 & 0.107 & 55.8  &  0.4399 $\pm$ 0.0870 $\pm$ 0.0224 \\
  1.844 & 0.225 & 0.107 & 95.6  &  0.4355 $\pm$ 0.1433 $\pm$ 0.0271 \\
  1.844 & 0.225 & 0.107 & 136.7 & -0.2736 $\pm$ 0.2804 $\pm$ 0.0166 \\
  1.844 & 0.225 & 0.107 & 182.7 &  0.5956 $\pm$ 0.3142 $\pm$ 0.0204 \\
  1.844 & 0.225 & 0.107 & 225.5 & -0.1065 $\pm$ 0.2739 $\pm$ 0.0270 \\
  1.844 & 0.225 & 0.107 & 263.0 & -0.3547 $\pm$ 0.1728 $\pm$ 0.0353 \\
  1.844 & 0.225 & 0.107 & 304.2 & -0.1088 $\pm$ 0.1008 $\pm$ 0.0263 \\
  1.844 & 0.225 & 0.107 & 340.0 & -0.1632 $\pm$ 0.0742 $\pm$ 0.0175 \\

@@

\begin{table}[!h]
   \begin{center}
      \begin{tabular}{||l|l|l|l|l||}
         \hline
 $<Q^{2}>$ & $<x_{B}>$ & $<-t>$ & $<\phi>$ & $A_{LU}$ $\pm$ stat. $\pm$ syst.\\
         \hline
  1.36 & 0.160 & 0.080 & 23.0  &  0.1884 $\pm$ 0.0891 $\pm$ 0.0263 \\
  1.36 & 0.160 & 0.080 & 57.0  &  0.2973 $\pm$ 0.0848 $\pm$ 0.0243 \\
  1.36 & 0.160 & 0.080 & 97.6  &  0.4928 $\pm$ 0.1155 $\pm$ 0.0394 \\
  1.36 & 0.160 & 0.080 & 138.7 &  0.2070 $\pm$ 0.1743 $\pm$ 0.0252 \\
  1.36 & 0.160 & 0.080 & 178.6 &  0.2466 $\pm$ 0.2021 $\pm$ 0.0371 \\
  1.36 & 0.160 & 0.080 & 222.1 & -0.1512 $\pm$ 0.1738 $\pm$ 0.0370 \\
  1.36 & 0.160 & 0.080 & 266.8 & -0.3610 $\pm$ 0.1363 $\pm$ 0.0403 \\
  1.36 & 0.160 & 0.080 & 300.6 & -0.2254 $\pm$ 0.0953 $\pm$ 0.0294 \\
  1.36 & 0.160 & 0.080 & 339.4 & -0.1889 $\pm$ 0.0795 $\pm$ 0.0281 \\

         \hline

  1.507 & 0.179 & 0.094 & 20.7  &  0.2291 $\pm$ 0.0874 $\pm$ 0.0267 \\
  1.507 & 0.179 & 0.094 & 55.4  &  0.3684 $\pm$ 0.0814 $\pm$ 0.0284 \\
  1.507 & 0.179 & 0.094 & 97.6  &  0.2149 $\pm$ 0.1193 $\pm$ 0.0307 \\
  1.507 & 0.179 & 0.094 & 141.4 &  0.0640 $\pm$ 0.2113 $\pm$ 0.0215 \\
  1.507 & 0.179 & 0.094 & 178.3 & -0.2712 $\pm$ 0.1944 $\pm$ 0.0360 \\
  1.507 & 0.179 & 0.094 & 219.0 &  0.1647 $\pm$ 0.2000 $\pm$ 0.0147 \\
  1.507 & 0.179 & 0.094 & 263.4 & -0.1991 $\pm$ 0.1284 $\pm$ 0.0283 \\
  1.507 & 0.179 & 0.094 & 303.8 & -0.1605 $\pm$ 0.0968 $\pm$ 0.0286 \\
  1.507 & 0.179 & 0.094 & 338.7 & -0.1862 $\pm$ 0.0839 $\pm$ 0.0201 \\
\hline                                                                
  1.610 & 0.193 & 0.127 & 21.9  &  0.0517 $\pm$ 0.0882 $\pm$ 0.0214 \\
  1.610 & 0.193 & 0.127 & 59.8  &  0.3527 $\pm$ 0.0934 $\pm$ 0.0204 \\
  1.610 & 0.193 & 0.127 & 96.4  &  0.3404 $\pm$ 0.1265 $\pm$ 0.0313 \\
  1.610 & 0.193 & 0.127 & 139.9 &  0.3285 $\pm$ 0.1842 $\pm$ 0.0203 \\
  1.610 & 0.193 & 0.127 & 179.5 &  0.6863 $\pm$ 0.1731 $\pm$ 0.0354 \\
  1.610 & 0.193 & 0.127 & 218.7 & -0.0617 $\pm$ 0.1731 $\pm$ 0.0189 \\
  1.610 & 0.193 & 0.127 & 261.1 & -0.2876 $\pm$ 0.1321 $\pm$ 0.0327 \\
  1.610 & 0.193 & 0.127 & 303.7 & -0.2077 $\pm$ 0.0882 $\pm$ 0.0280 \\
  1.610 & 0.193 & 0.127 & 336.8 & -0.2645 $\pm$ 0.0881 $\pm$ 0.0261 \\

@@

\chapter{Free proton beam-spin asymmetry interpolation} 
\label{app:free-proton-alu}
\section{Fitting the experimentally measured asymmetries} \label{fit_int} 
Following the discussion in section \ref{sec:Generalized_EMC}, comparing the 
coherent and the incoherent beam-spin asymmetries to free proton asymmetries 
reveal new information about the nuclear medium modifications. To construct 
such ratio, the published free proton asymmetries \cite{FX_BSA} have been used 
in this analysis, see figure \ref{fig:free-proton-alu}. The measured free 
proton $A_{LU}$ at $\phi = 90^{\circ}$ were fitted as a function of $-t$ for 
the different bins in $x_B$ and $Q^2$. Then, the parameters of the fits were 
parametrized as a function of $x_B$ assuming that the dependence on $Q^2$ is 
negligible, figure \ref{fig:free-proton-alu}. Finally, the free proton 
asymmetries were calculated at the same measured incoherent and coherent
kinematic values.  The statistical errors on the calculated asymmetries were 
calculated using the fit errors.\\

\begin{figure}[tpb]
\centering
\includegraphics[scale=0.85]{fig_Dec2016/F_ALU-proton-fits.pdf}
\caption{Black circles are the free proton beam-spin asymmetries at $\phi = 90 
   ^{\circ}$ as a function of $-t$ in different ($x_B, Q^2$) bins as measured 
   at CLAS-E1DVCS experiment. The solid red curves are fits to the free proton 
   asymmetries in the form $a_{0}*(\sqrt{t}-a_{1})*e^{a_{2}*\sqrt{t} - a_{3}}$.
   Blue points are the interpolated points corresponding for the incoherent 
points presented in this analysis. The red points stand for the extrapolated 
free proton asymmetries at the measured coherent kinematics.}
\label{fig:free-proton-alu}
\end{figure}
